---
title: "Practical Machine Learning Course Project"
output: html_document
---

The purpose of this work is to analyze personal activity data collected by devices like Jawbone Up, Nike FuelBand, and Fitbit, and to build a model for predicting the manner in which people did the exercises.

Original data was taken from http://groupware.les.inf.puc-rio.br/har.

##Data Processing

Loading data replacing empty values with NA:
```{r}
rawTrainData <- read.csv('pml-training.csv', na.strings=c("NA",""))
```

Calculating number of NA values in columns:
```{r}
nas <- colSums(!is.na(rawTrainData))
summary(nas)
```

Removing columns with too many NA:
```{r}
trainData <- rawTrainData[, nas > 500]
```

Removing columns which don't contain usefull information for prediction:
```{r}
removeIndex <- grep("timestamp|X|user_name|new_window", names(trainData))
trainData <- trainData[, -removeIndex]
```

Number of observations and variables in processed data:
```{r}
dim(trainData)

```

## Prediction Model

Random Forests are used as the prediction model.

Cross validation for tuning parameters of the model:
```{r}
library(caret)
fitControl <- trainControl(method="cv", number=4)
```

Separating data for "training" and "testing"" to estimate out sample error:
```{r}
inTraining <- createDataPartition(trainData$classe, p=.75, list=FALSE)
training <- trainData[inTraining,]
testing <- trainData[-inTraining,]
```

Training using selected model and cross validation:
```{r}
set.seed(12345)
modFit <- train(classe~., data=training, method="rf")#, trControl=fitControl)
```

## Calculating out sample error

Values predicted by the model:
```{r}
predicted <- predict(modFit, newdata=testing)
```

Comparing predicted data with testing subset:
```{r}
mx <- confusionMatrix(predicted, testing$classe)
mx$overall
```
Accuracy is , estimated sample error is .

